%
% Halaman Abstract
%
% @author  Andreas Febrian
% @version 2.2.0
% @edit by Ichlasul Affan
%

\chapter*{ABSTRACT}
\singlespacing

\noindent \begin{tabular}{l l p{11.0cm}}
	Name & : & Rifqi Rahmatuloh \\
	Study Program & : & Information Systems \\
	Title & : & Development of Attendance Management Dashboard and Teacher Leave System at Pondok Modern Al-Ghozali \\
	Counselor & : & Ichlasul Affan, S.Kom., M.Kom. \\
\end{tabular}

\vspace*{0.5cm}

\noindent This software development project aims to digitize the teacher attendance management process at Pondok Modern Al-Ghozali. Previously, attendance data processing relied on manual handling of fingerprint machine outputs, which was time-consuming and inefficient. In addition, the teacher leave process required direct coordination that often caused delays. 

The intern served as both Project Manager and Fullstack Developer, responsible for managing the development process and implementing system features. The Scrum methodology was applied with weekly sprint cycles to ensure continuous progress and adaptability to stakeholder needs. Core development activities included project timeline planning, backend development using the Django framework, and structured data processing utilizing the Pandas library. 

The resulting system is a functional web-based application featuring a statistical attendance dashboard, automated XLS file processing, and WhatsApp-based leave notification integration. This project provided practical experience in technical team management and the implementation of complex business logic, while reinforcing academic knowledge in software engineering, database systems, and software project management.

\vspace*{0.2cm}

\noindent \textbf{Keywords:} backend development, Django, project management, internship.

\setstretch{1.4}
\newpage
